---
title: "Shiny BART"
author: "Nathaniel Phillips"
date: "18 January 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Task Description

This app runs the Balloon Analogue Risk Task (BART)

# Using the Application

*Coming soon* 

## Uploading data to Dropbox

In order to upload data to Dropbox, you must include a file called `droptoken.rds` containing your dropbox authentication token. This file must be in the same folder as the main application file `ShinyBanditMulti_app.R`. You can create this file by running the following:

```{r eval = FALSE}
install.packages("rdrop2")                 # install rdrop2 packagre
droptoken <- rdrop2::drop_auth()           # Will open a browser and ask you to login
saveRDS(droptoken, file = "droptoken.rds") # Save token as droptoken.rds
```

You can specify the folder to save your data in with the `outputDir` object (This object will later on be passed to the `rdrop2::drop_upload()` function when it is time to actually save the data). For example, `outputDir <- "ShinyApp/data"` will save the data to a data folder contained in a ShinyApp folder. 

## Emailing data



## Notes


